Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-04-05 document/ms.tex
discussing inverse-detection-frequency

\section{Synthetic catalogs}

>>>>

\section{Validation using synthetic catalogs}

To confirm that the probabilistic framework developed in the previous sections
provides correct inferences about the population of exoplanets given noisy
data, we'll start by generating synthetic catalogs and running our full
inference pipeline on those data.
In this section, we also demonstrate the key benefits of our method over the
standard intuitive inverse-detection-efficiency procedure.

\paragraph{Inverse-detection-efficiency}
Authors in the exoplanet literature (for example, \citealt{howard, dressing,
petigura}) have built population level models using this procedure.
The basic idea is to make a histogram of planet candidates in the model where
each sample has a weight proportional to the inverse detection efficiency.
This method makes intuitive sense and, in the limit of infinitely precise
measurements, it is not wrong.
